Summary of the Iberian Bees Database

### 2022-02-27 Manuscript/Summary/Summary.Rmd
Update on Summary plots

@@

```{r echo=FALSE}
#barplot of top 10 species
data2 <- subset(data, accepted_name != "Apis mellifera")
default <- par()$mar
par(mar = c(10.1, 4.1, 4.1, 2.1))
barplot(head(sort(table(data2$accepted_name), decreasing = TRUE),20), las = 2, cex.names = 0.7)
#barplot(tail(sort(table(data2$accepted_name), decreasing = TRUE),20), las = 2, cex.names = 0.7)
par(mar = default)
```

@@

```{r echo=FALSE, warning=FALSE}
hist(data2$Year, main = "Most records are recorded since year 2000", 
     las = 1, xlab = "Year")
```

>>>>

\newpage

@@

```{r echo=FALSE}
#Prepare top 20 records
top_20 <- data %>% filter(!accepted_name=="Apis mellifera") %>% group_by(accepted_name) %>%
summarise(no_rows = length(accepted_name)) %>% 
arrange(-no_rows) %>% slice(1:20)
#Fix row position
top_20$accepted_name <- factor(top_20$accepted_name, levels = top_20$accepted_name)
#Plot
ggplot(top_20, aes(x=accepted_name, y=no_rows)) + 
geom_bar(stat = "identity", fill="#287D8EFF") +
theme_classic()+
theme(axis.text.x=element_text(angle=45, hjust=1, size=8, face = "italic")) +
ylab("Number of records") + 
xlab("Species") + 
ggtitle("Top 20 species") +
scale_y_continuous(expand = c(0, 0))

@@

```{r echo=FALSE, warning=FALSE}
data2 <- subset(data, accepted_name != "Apis mellifera")

hist(data2$Year, main = "Most records are recorded since year 2000", 
     las = 1, xlab = "Year")
```
